---
title: "Baseball Prediction"
author: "Marcelo Tibau"
date: "2 de janeiro de 2017"
output: 
  ioslides_presentation: 
    smaller: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Overview

This app uses data from the Joseph Adler data set. It comprises data from 2000 - 2008 for every major league baseball team, applies a linear model which predicts the number of runs scored by a team, and provide the prediction confidence interval based on some chosen variables.

A demo for the app can be found at: [https://marcelotibau.shinyapps.io/baseball-prediction/](https://marcelotibau.shinyapps.io/baseball-prediction/).

Source code for ui.R and server.R files are available on the GitHub repo: [https://github.com/marcelo-tibau/baseball-prediction](https://github.com/marcelo-tibau/baseball-prediction)

The inputs comprises of the following variables: Singles; Doubles; Triples;Home Runs; Walks; Hit by Pitch; Sacrifice Flies; Stolen Bases; and Caught Stealing. 

The adjustment will impact on the number of runs scored and the resulting confidence interval.

## Residuals Vs Fitted
The residual data of a linear regression model is the difference between the observed data of the dependent variable y and the fitted values y. If we find equally spread residuals around a horizontal line without distinct patterns, it's a good indication that we don't have non-linear relationships. 
```{r}
library(nutshell)
library(lattice)
data("team.batting.00to08")
runs.mdl <- lm(
  formula=runs~singles+doubles+triples+homeruns+
    walks+hitbypitch+sacrificeflies+
    stolenbases+caughtstealing,
  data=team.batting.00to08)
```

## Residuals Vs Fitted (cont)

```{r}
plot(runs.mdl, 1)
```

## Normal Q-Q
The Q-Q plot, or quantile-quantile plot, is a graphical tool to help us assess if a set of data plausibly came from some theoretical distribution such as a Normal or exponential. If both sets of quantiles came from the same distribution, we should see the points forming a line that's roughly straight. 
```{r}
plot(runs.mdl, 2)
```